%Resume Creation
\documentclass[]{rohan-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Rohan}{Patil}
{%% \urlstyle{same}\href{http://debarghyadas.com}{debarghyadas.com}| \href{http://fb.co/dd}{fb.co/dd}\\
\href{mailto:rp520671@gmail.com}{rp520671@gmail.com.com} | +91 8452851690  
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Mumbai University}
\descript{Saraswati College of Engineering \\
Kharghar\\
BE in Computer Engineering}
\location{ Navi Mumbai,  Maharashtra }
GPA: 8.44 / 10 \\
Percentage: 74.18 \% \\
 Aug 2019 - Jul 2023
\sectionsep 
\vspace{6pt}
\subsection{St.Mary Convent High\\
School \& Jr. College}
\location{Uran, Maharashra \\
\descript{MSBSHSE (CLASS XII)}
Percentage : 57.69 \% \\
Feb 2019}
\sectionsep
\vspace{6pt}
\subsection{Rotary English Medium\\
High School \& Jr. College}
\location{Uran, Maharashra \\
\descript{MSBSHSE (CLASS X)}
Percentage : 74.40 \% \\
Mar 2017 }

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://www.facebook.com/profile.php?id=100015914148004}{\bf rohan} \\
Github:// \href{https://github.com/rp520671}{\bf rp520671} \\
LinkedIn://  \href{www.linkedin.com/in/rohan-patil-8b860a201}{\bf rohan-patil} \\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Information Retrieval \\
Big Data Analytics \\
Data Warehousing and Mining \\\
Natural language Processing \\
Machine Learning\\
Operating Systems \\
Artificial Intelligence \\
Computer Graphics \\
Computer Networks\\
Database Management System\\
Cryptography and System Security\\
Quantitative Analysis\\
Microprocessors \\


\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Teravista.io Pvt .Ltd}
\descript{| Trainee -Software Developer }
\location{Apr 2023 - Jun 2023 | Andheri(East), Mumbai - 400072}
\sectionsep

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked with design teams and Senior Software Engineers to build   customized software products for consumers.
\item Providing solution of a problem given by client.
\item Handled scripting tasks for debugging and automation.
\item Worked closely with peers to identify issues and provide suitable resolutions.
\item Partnered with team members to learn best practices in software design.
\item Analyzed source code to identify functionality issues.
\item Coordinated project tasks among multiple departments.

\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Crime Rate Prediction and Analysis\\}
\location{Jul 2022 – May 2023 | Kharghar, Navi Mumbai}
 The \textbf{\href{https://github.com/rp520671/Crime}{CRPA}} Project is created to predict and analysis the crime going on the specific region as to decrease the crime going on that region by observation and helpful for official to work in ease.  
\sectionsep

\runsubsection{2D to 3D Dicom Image Conversion\\}
\location{Aug 2021 – May 2022 | Kharghar, Navi Mumbai}
 \textbf{\href{https://github.com/rp520671/SEM5-MINI-PROJECT}{2D-to-3d-dicom Image conversion}} project is created to convert medical dicom images (mri scans) from 2d to 3d as there should be ease while observing the diagnosed disease, this project mainly aims on fibrosis lung disease.\\
\sectionsep
\runsubsection{Azure Chatbot using FB Messenger as a Channel
  \\}
\location{Jan 2022 - Apr 2022 | Kharghar, Navi Mumbai}
The Azure chatbot  project is created for customer support service where chatbot replies to the consumers where the knowledge base is created using qna maker and chatbot is being deployed using microsoft azure and channel is selected where the chatbot will be actively working. 
 \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certification} 
\begin{tabular}{rll}
05/2020 - 06/2020 	       & Internship on Python.\\
07/2017 - 09/2017 &Maharashtra State Certification of Information Technology.\\
12/2018 - 12/2018  &One Day Hands-on Training Workshop on Robotics \\& at Vishwaniketan – Imeet, Khalapur.\\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
 \textbullet{} Java  \textbullet{} Python  
  \textbullet{} C/C++  \textbullet{} CSS \textbullet{} HTML \textbullet{} 
  React \textbullet{} Javascript \textbullet{} LaTex \\ 
\sectionsep
\subsection{Databases}
\textbullet{} mongoDB \textbullet{} MySQL
\sectionsep
\subsection{Web services}
\textbullet{} Amazon Web Services(AWS) \textbullet{} Microsoft Azure Web Services
\sectionsep
\subsection{Others}
\textbullet{} Problem Solving \textbullet{} Data Structures and Algorithms \textbullet{} SDLC Processes \\ 
\sectionsep




\end{minipage} 
\end{document}  \documentclass[]{article}
